Trends of SDR in Thessaloniki

### 2023-06-14 Article.Rmd
Commit 2023-06-14 11:17

@@

Using the mean daily SDR we produce the trends of each data set, as departure from the seasonal value.
Only for All-sky (Fig. \ref{fig:trendALL}) and Cloudy-sky (Fig. \ref{fig:trendCLOUD}) conditions, the statistical significance of the trends are acceptable (Tab. \ref{tab:trendtable}), to draw some conclusions.

@@

```{r trendCLOUD, echo=F, fig.cap="Anomaly (\\%) of the daily SDR relative to climatological values for 1993 - 2023. The black line shows the long term trend for cloud-sky conditions."}
knitr::include_graphics("./images/LongtermTrends-6.pdf")
```

@@

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.34\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics(c("./images/SzaTrends-13.pdf", "./images/SzaTrends-21.pdf"))
```

@@

## Zenith angle dependency and seasons of the year.

NOT INCLUDE?

.....

>>>>

## Clear sky identification

expanded discription

....

@@

Using the mean daily SDR we produce the trends of each data set, as departure from the seasonal value.
Only for All-sky (Fig. \ref{fig:trendALL}) <!--and Cloudy-sky (Fig. \ref{fig:trendCLOUD})--> conditions, the statistical significance of the trends are acceptable (Tab. \ref{tab:trendtable}), to draw some conclusions.

@@

<!-- ```{r trendCLOUD, echo=F, fig.cap="Anomaly (\\%) of the daily SDR relative to climatological values for 1993 - 2023. The black line shows the long term trend for cloud-sky conditions."} -->
<!-- knitr::include_graphics("./images/LongtermTrends-6.pdf") -->
<!-- ``` -->

@@

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.30\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
cat(" space ")     
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

```{r szatrends2, results="asis", echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.30\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
cat("\\ \n")     
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

@@

<!-- \FloatBarrier -->
<!-- 
## Zenith angle dependency and seasons of the year.
-->
